An Million Transcriptome Ocular Meta-Atlas for Discovery and Development

### 2020-11-09 manuscript_00.Rmd
add nmi plot

```{r supFig1, fig.width=4, fig.height=7, out.width=300, fig.cap=supFig1_cap, echo=FALSE, message = FALSE}
supFig1_cap <- supFig_cap(name='supFig1_cap', caption =  'The left bar delineates the number of cells for each organism - technology combination. The right bar specifies the number of each cells in each post QC category. In silico doublets were identified with scrublet and DoubletDetector.')

@@

source('figs_and_tables/fig2__integrationPerf.R')
cowplot::plot_grid(
  cowplot::plot_grid(lisi + theme(legend.position="none"), silhouette, nrow = 1), 
  cowplot::plot_grid(ari, legend, rel_widths = c(1,0.2), ncol = 2), 
  nrow = 2)
```

>>>>

@@

source('figs_and_tables/fig2__integrationPerf.R')
cowplot::plot_grid(
  cowplot::plot_grid(lisi + theme(legend.position="none"), silhouette, NULL, rel_widths = c(1,1,0.2), nrow = 1, labels = c('A' ,'B')), 
  cowplot::plot_grid(ari, nmi, legend, rel_widths = c(1,1, 0.2), ncol = 3, labels = c('C', 'D')), 
  nrow = 2)
```
